### 2017-04-06 Ben_Manuscripts/XSEDE/bridges_2017/proposed_work.tex
updated XSEDE

We repeated scaling studies with the same system using the GPU-enabled 
GROMACS 2016 which was compiled for optimal use with NVIDIA Tesla K80
accelerators. On Bridges we obtain 58 ns/day for the 66K atom system
using 4 GPUs and 28 cores. Simulating the solvated configuration, we
obtain 56.4 ns/day on 4 GPUs and 28 cores. Simulating the 265K atom 
system we obtain 10.1 ns/day on 4 GPUs and 28 cores.

>>>>

We repeated scaling studies with the same system using GPU-enabled 
GROMACS 2016 which was compiled for optimal use with NVIDIA Tesla K80
accelerators. On Bridges we obtain 58 ns/day, 56.4 ns/day and 10.1 ns/day
for the 66K, 100K and 256K atom systems respectively. Although the system
scales nearly linearly for greater than 4 GPUs in all cases, additional
GPUs require more than 1 node which has signficantly extended queue wait
times in our experience. It is preferable to run jobs longer on one GPU
for a long time than to delay a job from starting but have it run for a
shorter time. Since trajectory files are written while simulating, it
is beneficial to check progress and cancel jobs which show no value.
We plan to work with PSC to compile a version of gromacs that is performs
optimally with the
